Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2020-05-06 Manuscript/manuscript.Rmd
methods edits (comparing called v predicted boundaries section)

## Comparing Called vs Predicted TAD boundaries

To evaluate biological significance of our predictions, we evaluated the average signal profile of CTCF, RAD21, SMC3, and ZNF143 centered on the predicted TAD boundaries. The signal proviles were plotted using the `EnrichedHeatmap` R package [??? Add version and citation]. Furthermore, we compared the [??? log2?] distance between TAD boundaries and CTCF, RAD21, SMC3, and ZNF143 binding sites using Wilcoxon Rank-Sum test.

Under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms. Boundaries were flanked by resolution and overlaps were evaluated using Venn diagrams [??? Package?] and Jaccard index defined as

@@

where A and B are sets of genomic regions.

>>>>

## Comparing called vs predicted boundaries

Next, we evaluated the biological significance of our predicted boundaries with respect to the enrichment of several known molecular drivers of 3D chromatin architecture including CTCF, RAD21, SMC3, and ZNF143 ChIP-Seq peaks. Enrichmed heatmaps were used to compare preciseTAD boundaries to both ARROWHEAD and PEAKACHU called boundaries using the `EnrichedHeatmap` R package (version 1.14.0) [@gu2018enrichedheatmap]. Furthermore, we compared the $log_2$ [??? log2?] distance between TAD boundaries and the same top predictive transcription factor binding sites using Wilcoxon Rank-Sum test.

Under the hypothesis that TAD boundaries are highly concerved across cell types [@dixon2012topological; @nora2012spatial; @dixon2015chromatin; @rao20143d; @Schmitt2016aa], we assessed the conservation of our predicted TAD boundaries across cell types and prediction algorithms. Boundaries were flanked by resolution and overlaps were visualized using Venn diagrams from the `Vennerable` R package (version 3.1.0) [??? Package?;!!!added] and evaluated using the Jaccard index defined as

@@

where A and B represent genomic regions created by flanking called and predicted boundaries.
